---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# heapsofpapers

<!-- badges: start -->
<!-- badges: end -->

The goal of `heapsofpapers` is to make it really easy to politely get, well, heaps of papers. For instance, you may want to understand the state of open code and open data across a bunch of different pre-print repositories, e.g. Collins and Alexander, 2021. In that case you need a way to quickly get heaps of papers. 

Essentially the main function in the package is a wrapper around `purrr::walk2` and `utils::download.file`, but there are a bunch of small things that make it handy to use instead of rolling your own each time. For instance, the package automatically slows down your requests by 5-10 seconds, it also prints where it is up to.


## Installation

You can `heapsofpapers` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("RohanAlexander/heapsofpapers")
```

## Example

Here is an example of getting two papers from socarxiv:

```{r example, eval = FALSE}
library(heapsofpapers)
two_pdfs <-
  tibble::tibble(
    locations_are = c("https://osf.io/preprints/socarxiv/z4qg9/download",
                      "https://osf.io/preprints/socarxiv/a29h8/download"),
    save_here = c("~/competing_effects_on_the_average_age_of_infant_death.pdf",
                  "~/cesr_an_r_package_for_the_canadian_election_study.pdf")
    )

heapsofpapers::get_these_and_save_them(two_pdfs$locations_are, two_pdfs$save_here)
```


## Roadmap

- Make the length of the pause dependent on the size of the file that is downloaded, by default. Allow the user to specify how long they would like to wait.
- Make the printing of the message again optional, or every X or similar, as specified by the user.


## Citation

Please cite the package if you use it: Alexander, Rohan, and Annie Collins, 2021, 'heapsofpapers: Easily get heaps of papers' 6 March, https://github.com/RohanAlexander/heapsofpapers.




